---
title: main title
subtitle: A simple report that shows the capabilities of quarto and typst
author: the name of the author
date: 23 Feb 2024
lof: true
version: 0.1
format:
  medstata-typst: default
keep-typ: false
execute:
  echo: true
  warning: false
---




# Introduction to Quarto with Typst

This document demonstrates various features of Quarto with R integration, using Typst as the PDF rendering engine. Typst provides a more modern and intuitive alternative to LaTeX for PDF generation.

## Basic Markdown Features

Quarto supports all standard markdown formatting:

- **Bold text** and *italic text*
- Lists like this one
- [Hyperlinks](https://quarto.org/)
- Images, tables, and more

## Mathematical Expressions

You can include inline math like $E = mc^2$ or display equations:

$$
f(x) = \int_{-\infty}^{\infty} \hat{f}(\xi) e^{2\pi i \xi x} d\xi
$$

Typst's math syntax is fully compatible with LaTeX math, making the transition seamless.

# Code Execution Features

## Basic R Code

```{r}
# Simple calculation
2 + 2

# Creating a vector
numbers <- c(10, 20, 30, 40, 50)
mean(numbers)
```

## Data Visualization

```{r}
#| label: fig-scatter
#| fig-cap: "Scatter plot of mpg vs. disp"
#| fig-width: 8
#| fig-height: 5

library(ggplot2)

ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point(aes(color = factor(cyl))) +
  geom_smooth(method = "lm") +
  labs(
    title = "Relationship Between Engine Displacement and Fuel Efficiency",
    x = "Displacement (cu.in.)",
    y = "Miles Per Gallon",
    color = "Cylinders"
  ) +
  theme_classic()
```

## Tables

```{r}
#| label: tbl-summary
#| tbl-cap: "Summary statistics by cylinder count"

library(dplyr)
library(knitr)

mtcars %>%
  group_by(cyl) %>%
  summarize(
    Count = n(),
    `Mean MPG` = mean(mpg),
    `Mean HP` = mean(hp),
    `Mean Weight` = mean(wt)
  ) %>%
  kable()
```

# Typst-Specific Features

## Custom Styling with Typst

Quarto with Typst allows for custom styling using Typst syntax. You can include raw Typst commands using the `typst` engine:

```{=typst}
#let highlight(content) = {
  box(
    fill: yellow.lighten(80%),
    inset: (x: 3pt, y: 0pt),
    outset: (y: 3pt),
    radius: 2pt,
    content
  )
}

#highlight[This text is highlighted with custom Typst styling!]
```

## Font Customization

```{=typst}
#set text(font: "Linux Libertine", size: 11pt)


This paragraph will be rendered with Linux Libertine font in the PDF output.
```

## Advanced Layout with Typst

```{=typst}
#grid(
  columns: (1fr, 1fr),
  gutter: 1em,
  [
    #set par(leading: 0.65em)
    *Column 1*
    
    This is content in the first column. Typst makes it easy to create multi-column layouts.
  ],
  [
    #set par(leading: 0.65em)
    *Column 2*
    
    This is content in the second column. You can have different content here.
  ]
)
```

# Standard Quarto Features

## Cross-References

You can reference figures (see @fig-scatter) and tables (see @tbl-summary) using their labels.

## Callouts

::: {.callout-note}
This is a note callout block.
:::

::: {.callout-warning}
This is a warning callout block.
:::

::: {.callout-tip}
## Tip with a Title
This is a tip with a custom title.
:::

## Tabsets (HTML only)

::: {.panel-tabset}
### Tab 1

Content for the first tab goes here.

### Tab 2

```{r}
#| fig-cap: "Distribution of MPG"
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(bins = 10, fill = "steelblue") +
  theme_classic() +
  labs(title = "Distribution of MPG")
```

### Tab 3

Some additional text content.
:::

Note that tabsets are primarily an HTML feature and may not render the same way in PDF output.

# Plots

##  Plots 

```{r}
#| warning: false
#| message: false



p <- ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl), size = hp)) +
  geom_point(alpha = 0.3) +
  labs(
    title = "Interactive Car Data Plot",
    x = "Weight (1000 lbs)",
    y = "Miles Per Gallon",
    color = "Cylinders",
    size = "Horsepower"
  ) +
  theme_classic()
p
```

## Data Tables

```{r}

```

Note that interactive elements will only work in the HTML output.

# Typst-Specific YAML Options

This document demonstrates various Typst-specific YAML header options:

- `engine: typst` - Specifies Typst as the PDF rendering engine
- `typst-template: default` - Uses the default Typst template
- `margin` - Sets custom page margins
- `fontsize` - Sets the base font size

# Conclusion

Quarto with Typst provides a powerful system for creating dynamic documents that combine code, results, and narrative text, with the added benefit of modern PDF typesetting. This example showcases just a few of its many features.

## References {.unnumbered}

::: {#refs}
:::